FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-19 NewVersion/sections/Auxiliary.tex
section 4.2 added figures and corresponding text

\subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
\haoyuan{Visualize findorigin and findoverride with some figures.}
We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and
along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
the overridden interfaces will be filtered out.

@@

@@

\begin{flalign*}
	& \rhd \textit{Definition of } \mostSpecificOverride(m, I, J): & \\
	& \bullet \mostSpecificOverride(m, I, J) = \prune(overrides) & \\
	& \indent\indent \textrm{with: } overrides = \{K \mid \subt{I}{K}, \; \subt{K}{J} \textrm{ and } K[m\ \kwoverride\ J] \textrm{ is defined} &
\end{flalign*}
By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
\begin{itemize}
	\item It is between $I$ and $J$;
	\item It hierarchically overrides $J.m$;
	\item Any subtype of it does not belong to the same set.
\end{itemize}

>>>>

\subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
\haoyuan{Visualize findorigin and findoverride with some figures.}
We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined. As shown in Figure~\ref{fig:findOrigin}(left), interfaces in this set should be above interface $I$ and along path $J$. ``Along path $J$'' means the interface should be either a subtype or a super type of $J$, visually, it should locate between $J$ and $I$ or above $J$. Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
the overridden interfaces will be filtered out.

@@

\begin{figure*}[t]
  % \nocaptionrule
  % \centering
  \centering
  \begin{minipage}[t]{0.55\textwidth}
  \includegraphics[width=1cm]{pics/P10.pdf}
  \end{minipage}
  \centering
  \hspace*{2pt}
  \begin{minipage}[t]{0.35\textwidth}
  \includegraphics[width=1cm]{pics/P9.pdf}
  \end{minipage}  
  \caption{UMLs illustrating \mostSpecific(left) and \mostSpecificOverride(right)}\label{fig:findOrigin}
\end{figure*}

@@

\begin{flalign*}
	& \rhd \textit{Definition of } \mostSpecificOverride(m, I, J): & \\
	& \bullet \mostSpecificOverride(m, I, J) = \prune(overrides) & \\
	& \indent\indent \textrm{with: } overrides = \{K \mid \subt{I}{K}, \; \subt{K}{J} \textrm{ and } K[m\ \kwoverride\ J] \textrm{ is defined} &
\end{flalign*}
By the definition, as shown in Figure~\ref{fig:findOrigin}, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
\begin{itemize}
	\item it is between $I$ and $J$;
	\item it hierarchically overrides $J.m$;
	\item any subtype of it does not belong to the same set.
\end{itemize}
